# Empirical data
## Missing values
(ref:overview-table-missing-by-task-kathrin) Missing values of different algorithms by task
```{r overview-table-missing-by-task-kathrin, tab.cap=paste("(ref:overview-table-missing-by-task-kathrin)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_missing_by_task_kathrin)
```

(ref:overview-table-missing-by-filter-kathrin) Missing values of different algorithms by filter setting
```{r overview-table-missing-by-filter-kathrin, tab.cap=paste("(ref:overview-table-missing-by-filter-kathrin)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_missing_by_filter_kathrin)
```

## Reliability
(ref:overview-table-rel-by-task-kathrin) Reliability of different algorithms by task
```{r overview-table-rel-by-task-kathrin, tab.cap=paste("(ref:overview-table-rel-by-task-kathrin)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_rel_by_task_kathrin)
```

(ref:overview-table-rel-by-filter-kathrin) Reliability of different algorithms by filter setting
```{r overview-table-rel-by-filter-kathrin, tab.cap=paste("(ref:overview-table-rel-by-filter-kathrin)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_rel_by_filter_kathrin)
```

## Validity
(ref:overview-table-icc-by-task-kathrin) Validity of different algorithms by task
```{r overview-table-icc-by-task-kathrin, tab.cap=paste("(ref:overview-table-icc-by-task-kathrin)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_icc_by_task_kathrin)
```

(ref:overview-table-icc-by-filter-kathrin) Validity of different algorithms by filter setting
```{r overview-table-icc-by-filter-kathrin, tab.cap=paste("(ref:overview-table-icc-by-filter-kathrin)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_icc_by_filter_kathrin)
```

# Simulation
(ref:overview-table-icc-by-filter-simulation) Validity of different algorithms by filter setting
```{r overview-table-icc-by-filter-simulation, tab.cap=paste("(ref:overview-table-icc-by-filter-simulation)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_icc_by_filter_simulation)
```

# Linear Simulation
(ref:overview-table-icc-by-method-simulation-linear) Validity of different algorithms by method
```{r overview-table-icc-by-method-simulation-linear, tab.cap=paste("(ref:overview-table-icc-by-method-simulation-linear)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_icc_simulation_linear)
```

(ref:overview-table-icc-by-filter-simulation-linear) Validity of different algorithms by filter setting
```{r overview-table-icc-by-filter-simulation-linear, tab.cap=paste("(ref:overview-table-icc-by-filter-simulation-linear)"), tab.pos = "h", out.width="75%"}
knit_print(overview_table_icc_by_filter_simulation_linear)
```